\documentclass[margin]{res}
\newsectionwidth{17ex}

\setlength{\parindent}{0in}
\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
% \setlength{\textheight}{11in}
\setlength{\textheight}{12.5in}
\setlength{\topmargin}{-0.7in}
\setlength{\textwidth}{6.5in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.7in}
\setlength{\evensidemargin}{-0.7in}



\newcommand{\ustc}{University of Science and Technology of China}
\newcommand{\hefei}{Hefei, Anhui, P.R.C}
\newcommand{\ustcsz}{Suzhou Institute for Advanced Study, USTC}
\newcommand{\itemmark}{$\bullet$\mbox{~~}}


\begin{document}

{\bfseries \huge Simin Yang}
\hfill
\begin{tabular}{l}
\textit{Mobile: } \texttt{+}86\texttt{-}159\texttt{-}0162\texttt{-}4698\\
\textit{E-mail: }{smyang.ustc@gmail.com}
\end{tabular}
\rule{\columnwidth}{1pt}

\section{Education}
\textbf{\ustc}, \hefei\\[2mm]
{\it School of Computer Science}\\
M.S., Computer Software and Theory \hfill {\bf Jul 2010}\\[1.5mm]
{\it Department of Mathematics}\\
B.S., Information and Computing Science \hfill{\bf Jul 2007}\\[1.5mm]
{\it Department of Statics and Finance}\\
Dual Degree, Finance \hfill {\bf Jul 2007}

\section{Experience}
\textbf{USTC-Yale Joint Research Center for High-Confidence Software, USTC.} {\em Research Assistant}\\[2mm]
{\em \large Certifying Compiler for a C-like Programming Language} \hfill {\bf Jul 2008 - Oct 2009}\\
\hspace*{\fill} {\em Funded by National Natural Science Foundation of China}\\
When programming, programmers will write the corresponding program specifications to describe the behavior of the program. With our certifying compiler, the source codes and the specifications will be compiled into the executable file and the proof. Users use the proof checker to check the proof, and then indirectly check the reliability of the program. All that users have to trust is only the proof checker.
\\[-2.5mm]
\begin{itemize}
\item Join in the back-end development, responsible for the conversion from AST to x86, the formal description of our abstract machine and the proof of the soundness of our system.

\item Designed and implemented the automatic proof generator of assembly - level in cooperation with others. Responsible for writing and debugging the general-purpose proof scripts for the x86 assembly instructions and successfully reduced the size of the generated proof by 10+ times.
\end{itemize}
\vspace{1mm}

{\em\large Automated Theorem Proving in Building High-confidence Software} \hfill \textbf{Jan 2009 - Aug 2009}\\
\hspace*{\fill} {\em Funded by National Natural Science Foundation of China}\\
At present, the verification conditions(VC) are often proved by hand, while most of automatic theorem provers only report the result but do not support the generation of the machine - checkable proof. If the automated theorem proving could be applied in program verification and implemented the prover that can automatically solves the VC and generates the machine - checkable proof, it will greatly simplify the proving of VC and broaden the application of the high confidence software.
\\[-2.5mm]
\begin{itemize}
\item Proposed an innovative method to manage the information about proving, including the proof segments and the records of proving actions, and then build the machine - checkable proof terms from the records; implemented all modules of the method.

\item Based on the improved Simplex algorithm and the above - mentioned method, designed and implemented an automated theorem prover for linear integer arithmetic, which outputs proof terms that can be checked by the proof assistant - Coq.
\end{itemize}
\vspace{1mm}

{\em Teaching Assistant}
\vspace{1mm}
\begin{itemize}
\item Discrete Mathematics and Its Applications, {\em School of Software Engineering}, USTC  \hfill {\bf 2008 - 2009, fall}

\item Principles of Compiler, {\em School of Computer Science}, USTC  \hfill {\bf 2007 - 2008, spring}
\end{itemize}
\vspace{2mm}

% {\bf USTC E-Business Technology Co., Ltd.} {\em Part-time intern}
% \hfill {\bf Feb 2007 - May 2007}
% \vspace{1mm}
% \begin{itemize}
% \item Group member of a J2EE-based project for building a web portal platform that provides customized features and personalized content.
% \item Using BEA WebLogic Portal, achieved individuality and customization.
% \end{itemize}

\section{Honors \& \quad Awards} 
\textbf{\ustc}, \hefei
\vspace{2mm}
\begin{itemize}
\item Outstanding Student Scholarship (Bronze) \hfill {\bf 2005}
\item San Pu Scholarship \hfill {\bf 2004}
\item Outstanding New Student Scholarship (Bronze)\hfill {\bf 2003}
\end{itemize}

\section{Language \& \quad Technical Skills}
\begin{itemize}
\item CET-6. Good reading, writing and presentation skills in English;
\item Experienced with automated theorem proving and compiler;
\item Coding experience with functional programming (SML/OCaml), Coq, C and so on;
\item General knowledge about Linux, server and others.
\end{itemize}

\section{Self Evaluation}
\begin{itemize}

\item Conscientiously, absorbedly work in a planned and order way; emphasize details;
\item A quick learner to new ideas and new technologies;
\item Cooperate well with colleagues, and enjoy discussing and sharing of research ideas.

\end{itemize}

\end{document}
