\documentclass[margin]{res}
\usepackage{xltxtra,fontspec,xunicode}
\usepackage[slantfont,boldfont]{xeCJK}
\usepackage{zhspacing}
\newsectionwidth{17ex}

\setCJKmainfont[BoldFont={SimHei}]{SimSun} % 缺省中文字体
\setCJKmonofont{WenQuanYi Micro Hei Mono} % 设置等宽字体
\setmainfont{Liberation Sans} % 英文衬线字体
\setmonofont{Liberation Mono} % 英文等宽字体
\setsansfont{Liberation Sans} % 英文无衬线字体
\setCJKfamilyfont{Hei}{WenQuanYi Zen Hei}

\setlength{\parindent}{0in}
\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
% \setlength{\textheight}{11in}
\setlength{\textheight}{12.5in}
\setlength{\topmargin}{-0.7in}
\setlength{\textwidth}{6.5in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.7in}
\setlength{\evensidemargin}{-0.7in}



\newcommand{\ustc}{中国科学技术大学}
\newcommand{\taomee}{上海淘米网络科技有限公司}
\newcommand{\ustcsz}{中国科学技术大学苏州研究院}
\newcommand{\itemmark}{$\bullet$\mbox{~~}}


\begin{document}

{\bfseries \huge 杨\ 思\ 敏}
\hfill
\begin{tabular}{l}
    手机： {18621809050}\\
    邮箱： {smyang.ustc@gmail.com}
\end{tabular}
\rule{\columnwidth}{1pt}


\section{\Large 工作经历}
{\bf \large \taomee}，
中国最为领先的儿童娱乐媒体公司，NYSE上市企业。
\hfill 2010年7月至今\\[1mm]
\begin{itemize}
    \item {\bf 运维系统}，C/C++ 后台开发工程师 
        \hfill 2012年07月至今\\[1mm]
        该系统综合了Ganglia的实时状态图、Nagios的异常告警，
        整合了资产管理和数据库管理等功能，
        以方便运维人员对线上500余台服务器和交换机进行管理。
        本人全面负责运维系统的后台研发工作，带领三个人的小团队，
        使用统一的异步服务器框架，快速构建具有集中分发、透明代理等模块的多层次网络架构。
        期间还辅导一名应届生顺利转正。
        \\
    \item {\bf 数据分析}，Linux 后台开发工程师
        \hfill 2012年12月至今\\[1mm]
        使用Hadoop对线上玩家的登录、充值、消费等数据进行分析。
        对每个游戏产品，给出PV/UV、新增/活跃/留存/回流、付费ARPU/渗透率等关键数据，
        为线上游戏的科学决策和品质运营提供服务。
        负责编写数据分析用的部分Mapper/Reducer代码，
        及时比照检查结果数据的准确性。
        \\
    \item {\bf 射击类竞技页游《凯特战争》}，C/C++ 后台开发工程师 
        \hfill 2011年11月 - 2012年06月\\[1mm]
        《凯特战争》是淘米首款采用与《魔兽世界》类似的大区小服结构的页游。
        期间，接触到多层次的网络后台系统架构，学习了健壮性可扩展性系统设计。
        特别是使用epoll模型的异步服务器框架后，数据存取、业务处理和数据转发的分层次设计。
        通过降低模块之间的耦合性，提升灵活度，来适应运营中大区小服开荒、合并的需求。
        \\
    \item {\bf 社区游戏《摩尔斗斗》}，C/C++ 后台开发工程师 
    \hfill 2010年12月 - 2011年11月\\[1mm]
        《摩尔斗斗》是国内首款儿童社区游戏，
        在人人网、新浪微游戏、开心网和淘米校巴等平台运营。其中，
        在人人网一度达到2.5万日活跃用户，位居最活跃排行榜第一，
        销售排行榜前三，被推荐为热门游戏。
        从游戏立项到研发上线，再到后期运营拓展，经历了完整的游戏生命过程，
        从对游戏后台零概念开始，逐步学习成长为后台负责人。
        \\
   \item {\bf 流量统计系统}，C/C++ 软件开发工程师 
       \hfill 2010年07月 - 2010年12月\\[1mm]
       实现与Google Analytics类似的PV/UV/IP分类统计功能。
       对公司的所有对外web页面，提供精确到分、延迟不超过5分钟的实时数据，
       以及15分钟、1小时、1天等精度的汇总数据。
       使用分布式文件系统MooseFS解决了大量数据的分布式存取、处理的问题。
       应用mmap和红黑树算法，提升了大量Key-Value数据的实时统计效率。
       该项目获得领导的一致好评。



\end{itemize}

\section{\Large 教育背景}
{\bf \large \ustc}\\[1mm]
\begin{itemize}
    \item {\bf 硕士，计算机软件与理论}，计算机科学与技术学院 \hfill 2007年09月 - 2010年06月
    \item {\bf 学士，信息与计算科学}，数学系 \hfill 2003年09月 - 2007年06月
    \item {\bf 双学位，金融学}，统计与金融系 \hfill 2005年01月 - 2007年06月
\end{itemize}


\section{\Large 专业技术}
\begin{itemize}
    \item CET-6，较好的英文读写能力；
    \item 掌握C/C++，十万行以上代码经验，熟悉Shell编程，了解Python、PHP和Java编程
    \item 掌握MySQL编程，了解Memcache、Berkeley DB和Hadoop的基本用法
    \item 两年以上Linux环境开发经验，能熟练使用vim/make/gdb/valgrind等开发、调试、测试工具
    \item 熟悉Linux下网络编程，了解编译器技术，特别是后端的代码生成和优化
    \item 掌握Linux系统常用应用服务配置、维护，知晓常用的性能调优方法
\end{itemize}

\section{\Large 自我评价}
\begin{itemize}
    \item 工作认真，注重细节，信守承诺，勇于开拓创新；
    \item 兴趣广泛，好奇心强，喜欢钻研新技术，学习能力突出，接受新鲜事物较快；
    \item 团队意识良好，主动承担相关责任，并积极配合他人按时按质完成工作，保证团队进度。 
\end{itemize}


\section{\Large 奖励荣誉} 
{\bf \taomee}。2010年{\bf 最佳新人奖}\\
{\bf \ustc}。2005年优秀学生奖学金；2004年三浦奖学金；2003年优秀新生奖学金

\section{\Large 个人信息}
    男，1985年10月生，目前居住在上海

\end{document}

%\section{Experience}
%\textbf{USTC-Yale Joint Research Center for High-Confidence Software, USTC.} {\em Research Assistant}\\[2mm]
%{\em \large Certifying Compiler for a C-like Programming Language} \hfill {\bf Jul 2008 - Oct 2009}\\
%\hspace*{\fill} {\em Funded by National Natural Science Foundation of China}\\
%When programming, programmers will write the corresponding program specifications to describe the behavior of the program. With our certifying compiler, the source codes and the specifications will be compiled into the executable file and the proof. Users use the proof checker to check the proof, and then indirectly check the reliability of the program. All that users have to trust is only the proof checker.
%\\[-2.5mm]
%\begin{itemize}
%\item Join in the back-end development, responsible for the conversion from AST to x86, the formal description of our abstract machine and the proof of the soundness of our system.

%\item Designed and implemented the automatic proof generator of assembly - level in cooperation with others. Responsible for writing and debugging the general-purpose proof scripts for the x86 assembly instructions and successfully reduced the size of the generated proof by 10+ times.
%\end{itemize}
%\vspace{1mm}

%{\em\large Automated Theorem Proving in Building High-confidence Software} \hfill \textbf{Jan 2009 - Aug 2009}\\
%\hspace*{\fill} {\em Funded by National Natural Science Foundation of China}\\
%At present, the verification conditions(VC) are often proved by hand, while most of automatic theorem provers only report the result but do not support the generation of the machine - checkable proof. If the automated theorem proving could be applied in program verification and implemented the prover that can automatically solves the VC and generates the machine - checkable proof, it will greatly simplify the proving of VC and broaden the application of the high confidence software.
%\\[-2.5mm]
%\begin{itemize}
%\item Proposed an innovative method to manage the information about proving, including the proof segments and the records of proving actions, and then build the machine - checkable proof terms from the records; implemented all modules of the method.

%\item Based on the improved Simplex algorithm and the above - mentioned method, designed and implemented an automated theorem prover for linear integer arithmetic, which outputs proof terms that can be checked by the proof assistant - Coq.
%\end{itemize}
%\vspace{1mm}

%{\em Teaching Assistant}
%\vspace{1mm}
%\begin{itemize}
%\item Discrete Mathematics and Its Applications, {\em School of Software Engineering}, USTC  \hfill {\bf 2008 - 2009, fall}

%\item Principles of Compiler, {\em School of Computer Science}, USTC  \hfill {\bf 2007 - 2008, spring}
%\end{itemize}
%\vspace{2mm}

% {\bf USTC E-Business Technology Co., Ltd.} {\em Part-time intern}
% \hfill {\bf Feb 2007 - May 2007}
% \vspace{1mm}
% \begin{itemize}
% \item Group member of a J2EE-based project for building a web portal platform that provides customized features and personalized content.
% \item Using BEA WebLogic Portal, achieved individuality and customization.
% \end{itemize}

%\section{Self Evaluation}
%\begin{itemize}

%\item Conscientiously, absorbedly work in a planned and order way; emphasize details;
%\item A quick learner to new ideas and new technologies;
%\item Cooperate well with colleagues, and enjoy discussing and sharing of research ideas.

%\end{itemize}

